---
title: "P8105 Homework 1"
output: github_document
author: Shritama Ray
date: 9/22/2022
---

## Problem 1

Load the **penguins** dataset:

```{r load_penguins}
data("penguins", package = "palmerpenguins")
```

Size of the dataset:
```{r penguins_size}
nrow(penguins)
ncol(penguins)
```

Descriptive Statistics:
```{r descriptive_stats}
summary(penguins)
```

**Discussion:**
This dataset consists of a 344 row x 8 column tibble.
The variables are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. There are **3 species** of penguins represented, across **3 islands.** The mean flipper length of the penguins is **200.9 mm.** 

**Scatterplot of flipper length vs. bill length**
```{r load_tidyverse, message = FALSE}
#Load tidyverse library
```
```{r scatterplot, warning = FALSE}
library(tidyverse)
#Create scatter plot colored by species
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

# Section 2


